---
title: "Advanced JS Hooks & Events"
description: "Inject custom JavaScript, validation, or event logic beyond R—unlock the full power of SurveyJS events and lifecycle."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Advanced JS Hooks & Events}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Advanced JS Hooks & Events

- _Inject custom JavaScript to extend SurveyJS far beyond R defaults._
- _Validate, log, or react to user input with powerful event hooks._
- _Write only the body of your JavaScript function, as a string—see runnable examples below._
- _Tip: Always use just the function body (no `function(...) {}` wrapper), and check the browser’s JS console for errors._
- _For survey building blocks and theming, see the other vignettes._

---

## Table of Contents

- [What are JS Hooks?](#what-are-js-hooks)
- [Pre-Render Hook](#pre-render-hook)
- [Post-Render Hook](#post-render-hook)
- [Complete Hook](#complete-hook)
- [Custom Event Listeners](#custom-event-listeners)
- [Debugging and Tips](#debugging-and-tips)
- [Further Reference](#further-reference)

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 8
)
library(rsurveyjs)
```

---

## What are JS Hooks?

- Hooks let you insert custom JavaScript at key points in the survey lifecycle.
- Write just the **function body** (as a string), not a full `function() { ... }`.
- Hooks run in the browser. Use `console.log()` for debugging.

---

## Pre-Render Hook

**Runs before the survey is displayed.**  
Use for custom validation, event listeners, or setup logic.

### Example: Enforce minimum nickname length

```{r}
surveyjs(
  schema = list(
    title = "Nickname Check",
    questions = list(
      list(type = "text", name = "nickname", title = "Enter a nickname")
    )
  ),
  pre_render_hook = "
    survey.onValidateQuestion.add(function(sender, options) {
      if (options.name === 'nickname' && options.value.length < 4) {
        options.error = 'Too short';
      }
    });
  "
)
```

---

## Post-Render Hook

**Runs after the survey is rendered.**  
Use for custom DOM tweaks, styling, or logging.

### Example: Add a custom border

```{r}
surveyjs(
  schema = list(
    title = "Styled Survey",
    questions = list(
      list(type = "text", name = "name", title = "Your name?")
    )
  ),
  post_render_hook = "
    el.style.border = '2px dashed #888';
    console.log('Survey rendered:', el);
  "
)
```

---

## Complete Hook

**Runs when the survey is completed by the user.**  
Use to trigger alerts, send data, or fire custom analytics.

### Example: Show a thank-you alert

```{r}
surveyjs(
  schema = list(
    title = "Completion Alert",
    questions = list(
      list(type = "text", name = "email", title = "Your email?")
    )
  ),
  complete_hook = "
    alert('Thank you for completing the survey!');
  "
)
```

---

## Custom Event Listeners

Attach any [SurveyJS event](https://surveyjs.io/form-library/documentation/api-reference/survey-data-model#events) in a pre-render hook.

### Example: Log every value change

```{r}
surveyjs(
  schema = list(
    title = "Value Tracking",
    questions = list(
      list(type = "text", name = "email", title = "Your email?")
    )
  ),
  pre_render_hook = "
    survey.onValueChanged.add(function(sender, options) {
      console.log('Field changed:', options.name, options.value);
    });
  "
)
```

---

## Debugging and Tips

- Write only the function body (not `function() { ... }`).
- Use `console.log()` for debugging in your browser’s JS console.
- If your JS code errors, check the browser console for details.
- See all events: [SurveyJS Events Reference](https://surveyjs.io/form-library/documentation/api-reference/survey-data-model#events).

---

## Further Reference

- [SurveyJS Events API](https://surveyjs.io/form-library/documentation/api-reference/survey-data-model#events)
- See also: [Survey Schema Recipes](survey-schema-recipes.html), [Themes, Styling and Localization](themes-styling-and-localization.html)
