
---
title: "Question Types"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Question Types}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rsurveyjs)
```

# Question Type Examples

Below are usage examples of each supported question type in `rsurveyjs`. These correspond to the standard SurveyJS question types.

## Basic Inputs

### Text Input
```{r}
surveyjs(schema = list(
  title = "Text Input Example",
  questions = list(
    list(type = "text", name = "name", title = "What is your name?")
  )
))
```

### Comment Box
```{r}
surveyjs(schema = list(
  title = "Comment Box Example",
  questions = list(
    list(type = "comment", name = "feedback", title = "Please provide your feedback")
  )
))
```

### Rating
```{r}
surveyjs(schema = list(
  title = "Rating Example",
  questions = list(
    list(type = "rating", name = "experience", title = "Rate your experience")
  )
))
```

### Dropdown
```{r}
surveyjs(schema = list(
  title = "Dropdown Example",
  questions = list(
    list(type = "dropdown", name = "country", title = "Select your country", choices = list("USA", "Canada", "Mexico"))
  )
))
```

### Checkbox
```{r}
surveyjs(schema = list(
  title = "Checkbox Example",
  questions = list(
    list(type = "checkbox", name = "hobbies", title = "Select your hobbies", choices = list("Reading", "Sports", "Music"))
  )
))
```

### Radio Group
```{r}
surveyjs(schema = list(
  title = "Radio Group Example",
  questions = list(
    list(type = "radiogroup", name = "gender", title = "Select your gender", choices = list("Male", "Female", "Other"))
  )
))
```

### Boolean Toggle
```{r}
surveyjs(schema = list(
  title = "Boolean Example",
  questions = list(
    list(type = "boolean", name = "agree", title = "Do you agree?")
  )
))
```

### Image Picker
```{r}
surveyjs(schema = list(
  title = "Image Picker Example",
  questions = list(
    list(
      type = "imagepicker",
      name = "car",
      title = "Choose a car",
      choices = list(
        list(value = "ford", imageLink = "https://via.placeholder.com/100?text=Ford"),
        list(value = "bmw", imageLink = "https://via.placeholder.com/100?text=BMW"),
        list(value = "tesla", imageLink = "https://via.placeholder.com/100?text=Tesla")
      )
    )
  )
))
```

### File Upload
```{r}
surveyjs(schema = list(
  title = "File Upload Example",
  questions = list(
    list(type = "file", name = "resume", title = "Upload your resume")
  )
))
```

## Layout and Logic

### HTML Block
```{r}
surveyjs(schema = list(
  title = "HTML Example",
  questions = list(
    list(type = "html", name = "intro", html = "<h3>Welcome to the Survey!</h3><p>Please answer honestly.</p>")
  )
))
```

### Matrix
```{r}
surveyjs(schema = list(
  title = "Matrix Example",
  questions = list(
    list(
      type = "matrix",
      name = "satisfaction",
      title = "Rate your satisfaction",
      columns = list("Very Dissatisfied", "Dissatisfied", "Neutral", "Satisfied", "Very Satisfied"),
      rows = list("Quality", "Speed", "Support")
    )
  )
))
```

### Matrix Dropdown
```{r}
surveyjs(schema = list(
  title = "Matrix Dropdown Example",
  questions = list(
    list(
      type = "matrixdropdown",
      name = "performance",
      title = "Evaluate team performance",
      columns = list(
        list(name = "efficiency", title = "Efficiency", cellType = "dropdown", choices = list("Low", "Medium", "High")),
        list(name = "quality", title = "Quality", cellType = "dropdown", choices = list("Low", "Medium", "High"))
      ),
      rows = list(
        list(value = "john", text = "John"),
        list(value = "jane", text = "Jane")
      )
    )
  )
))
```

### Matrix Dynamic
```{r}
surveyjs(schema = list(
  title = "Dynamic Matrix Example",
  questions = list(
    list(
      type = "matrixdynamic",
      name = "education",
      title = "List your education history",
      columns = list(
        list(name = "degree", title = "Degree"),
        list(name = "institution", title = "Institution"),
        list(name = "year", title = "Year")
      ),
      rowCount = 1
    )
  )
))
```

### Multiple Text
```{r}
surveyjs(schema = list(
  title = "Multiple Text Example",
  questions = list(
    list(
      type = "multipletext",
      name = "contact",
      title = "Contact Information",
      items = list(
        list(name = "email", title = "Email"),
        list(name = "phone", title = "Phone Number")
      )
    )
  )
))
```

### Signature Pad
```{r}
surveyjs(schema = list(
  title = "Signature Pad Example",
  questions = list(
    list(type = "signaturepad", name = "signature", title = "Please sign below")
  )
))
```

### Expression (Calculated Value)
```{r}
surveyjs(schema = list(
  title = "Expression Example",
  questions = list(
    list(type = "text", name = "a", title = "Enter a number"),
    list(type = "text", name = "b", title = "Enter another number"),
    list(type = "expression", name = "sum", title = "Sum", expression = "{a} + {b}")
  )
))
```

## Panels, Lists, and Ranking
### Panel (Group)
```{r}
surveyjs(schema = list(
  title = "Panel Example",
  questions = list(
    list(
      type = "panel",
      name = "personal_info",
      title = "Personal Information",
      elements = list(
        list(type = "text", name = "first_name", title = "First Name"),
        list(type = "text", name = "last_name", title = "Last Name")
      )
    )
  )
))
```

### Panel Dynamic
```{r}
surveyjs(schema = list(
  title = "Dynamic Panel Example",
  questions = list(
    list(
      type = "paneldynamic",
      name = "employers",
      title = "Previous Employers",
      templateElements = list(
        list(type = "text", name = "company", title = "Company Name"),
        list(type = "text", name = "role", title = "Job Title")
      ),
      panelCount = 1
    )
  )
))
```

### Ranking
```{r}
surveyjs(schema = list(
  title = "Ranking Example",
  questions = list(
    list(
      type = "ranking",
      name = "priorities",
      title = "Rank your priorities",
      choices = list("Work", "Family", "Health", "Friends", "Hobbies")
    )
  )
))
```

## Sortable List
```{r}
surveyjs(schema = list(
  title = "Sortable List Example",
  questions = list(
    list(
      type = "sortablelist",
      name = "order_things",
      title = "Arrange these in preferred order",
      choices = list("Apples", "Bananas", "Cherries", "Dates")
    )
  )
))
```

## Static Content and Pickers
### Image Display
```{r}
surveyjs(schema = list(
  title = "Image Example",
  questions = list(
    list(
      type = "image",
      name = "promo_image",
      imageLink = "https://via.placeholder.com/300x100.png?text=Banner+Image"
    )
  )
))
```

## Date Picker
```{r}
surveyjs(schema = list(
  title = "Date Picker Example",
  questions = list(
    list(type = "date", name = "birthdate", title = "Select your birthdate")
  )
))
```

## Time Picker
```{r}
surveyjs(schema = list(
  title = "Time Picker Example",
  questions = list(
    list(type = "time", name = "alarm", title = "Set your alarm time")
  )
))
```
