---
title: "Shiny and Database Integration"
description: "Collect, update, and save survey responses interactively—including persistent storage and live updates in Shiny."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Shiny and Database Integration}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Shiny and Database Integration

- _Seamlessly embed SurveyJS forms in Shiny apps._
- _Capture, update, and persist survey responses—including live editing and database storage._
- _For custom JS hooks or frontend logic, see the [Advanced JS Hooks & Events](advanced-js-hooks--events.html) vignette._

---

## Table of Contents

- [Minimal Shiny Survey App](#minimal-shiny-survey-app)
- [Live Mode: Real-Time Updates](#live-mode-real-time-updates)
- [Dynamic Updates: Update Survey from Server](#dynamic-updates-update-survey-from-server)
- [Saving and Loading Responses with a Database](#saving-and-loading-responses-with-a-database)
- [Common Pitfalls & Further Reference](#common-pitfalls--further-reference)

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
library(rsurveyjs)
```

---

## Minimal Shiny Survey App

```{r minimal-shiny-app, eval=FALSE}
library(shiny)
library(rsurveyjs)

ui <- fluidPage(
  surveyjsOutput("mysurvey"),
  verbatimTextOutput("result")
)

server <- function(input, output, session) {
  output$mysurvey <- renderSurveyjs({
    surveyjs(
      schema = list(
        title = "Feedback",
        questions = list(
          list(type = "text", name = "name", title = "What is your name?"),
          list(type = "rating", name = "rating", title = "How would you rate us?")
        )
      )
    )
  })

  output$result <- renderPrint({
    input$mysurvey_data
  })
}

shinyApp(ui, server)
```

---

## Live Mode: Real-Time Updates

Use `live = TRUE` to get continuous feedback as the user fills out the form.

```{r, eval=FALSE}
ui <- fluidPage(
  surveyjsOutput("mysurvey"),
  verbatimTextOutput("live_output")
)

server <- function(input, output, session) {
  output$mysurvey <- renderSurveyjs({
    surveyjs(
      schema = list(
        title = "Live Feedback",
        questions = list(
          list(type = "text", name = "comment", title = "Your comment?")
        )
      ),
      live = TRUE
    )
  })

  output$live_output <- renderPrint({
    input$mysurvey_data_live
  })
}
```

- Use `input$<id>_data_live` for live data.
- Use `input$<id>_data` for final, completed responses.

---

## Dynamic Updates: Update Survey from Server

Use `updateSurveyjs()` to change schema, initial data, theme, or locale on the fly.

```{r, eval=FALSE}
ui <- fluidPage(
  surveyjsOutput("mysurvey"),
  actionButton("reload", "Switch Survey")
)

server <- function(input, output, session) {
  output$mysurvey <- renderSurveyjs({
    surveyjs(
      schema = list(
        title = "First Survey",
        questions = list(
          list(type = "text", name = "favorite", title = "Favorite color?")
        )
      )
    )
  })

  observeEvent(input$reload, {
    updateSurveyjs(session, "mysurvey", schema = list(
      title = "New Survey",
      questions = list(
        list(type = "rating", name = "satisfaction", title = "Rate your satisfaction")
      )
    ))
  })
}
```

---

## Saving and Loading Responses with a Database

Here’s a minimal example using `{DBI}` and SQLite for persistent storage.

```{r, eval=FALSE}
library(DBI)
library(RSQLite)
library(shiny)
library(rsurveyjs)

# Set up database connection (for demo: use temp file)
con <- dbConnect(RSQLite::SQLite(), "responses.sqlite")
if (!dbExistsTable(con, "survey_results")) {
  dbExecute(con, "CREATE TABLE survey_results (
    id INTEGER PRIMARY KEY AUTOINCREMENT,
    timestamp TEXT,
    name TEXT,
    rating INTEGER
  )")
}

ui <- fluidPage(
  surveyjsOutput("mysurvey"),
  actionButton("save", "Save Response"),
  tableOutput("responses")
)

server <- function(input, output, session) {
  output$mysurvey <- renderSurveyjs({
    surveyjs(
      schema = list(
        title = "Feedback",
        questions = list(
          list(type = "text", name = "name", title = "Your name?"),
          list(type = "rating", name = "rating", title = "Rate us")
        )
      )
    )
  })

  observeEvent(input$save, {
    dat <- input$mysurvey_data
    if (!is.null(dat)) {
      dbExecute(con, "INSERT INTO survey_results (timestamp, name, rating) VALUES (?, ?, ?)",
        params = list(Sys.time(), dat$name, dat$rating)
      )
    }
  })

  output$responses <- renderTable({
    dbGetQuery(con, "SELECT * FROM survey_results ORDER BY id DESC")
  })
}

onStop(function() dbDisconnect(con))
shinyApp(ui, server)
```

- Replace `"responses.sqlite"` with your desired file path or use another DBI-compatible backend.
- For production, sanitize and validate inputs appropriately.

---

## Common Pitfalls & Further Reference

- **Input IDs:**  
  - `input$mysurvey_data` is the completed form data.  
  - `input$mysurvey_data_live` is live-updating data (when `live = TRUE`).
- **Missing responses:**  
  - Always check `is.null(input$mysurvey_data)` before saving.
  - Ensure the survey “Complete” button is clicked to trigger saving.
- **More advanced features:**  
  - See [Advanced JS Hooks & Events](advanced-js-hooks--events.html) to react to completion or validation in the frontend.
- **Further Reading:**  
  - [SurveyJS documentation](https://surveyjs.io/form-library/documentation/)
  - [DBI documentation](https://dbi.r-dbi.org/)
  - [RSQLite documentation](https://rsqlite.r-dbi.org/)

