---
title: "Survey Schema Recipes"
description: "Copy-paste recipes for every survey building block: question types, validation, logic, and more."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Survey Schema Recipes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Survey Schema Recipes

_Build any survey in R using the power of [SurveyJS](https://surveyjs.io/)._  
_This vignette is a cookbook: copy, paste, and adapt as needed._

---

## Table of Contents

- [Single Question Types](#single-question-types)
- [Multiple Choice & Matrix](#multiple-choice--matrix)
- [Layout: Pages, Panels, Dynamic Forms](#layout-pages-panels-dynamic-forms)
- [Advanced: Validation, Logic, Quizzes](#advanced-validation-logic-quizzes)
- [Initial Values & Read-only Mode](#initial-values--read-only-mode)
- [Calculated Fields](#calculated-fields)
- [Static Content: Images & HTML](#static-content-images--html)
- [Further Reference](#further-reference)

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width = 8
)
library(rsurveyjs)
original_surveyjs <- get("surveyjs", envir = asNamespace("rsurveyjs"))
surveyjs <- function(...) original_surveyjs(..., width = "100%", height = "100%")
```

- Tip: Pass a JSON-compatible list to `surveyjs()` to render a survey.
- Tip: Results are only returned to R in a Shiny app—see the Shiny Integration vignette.
- Every example here is a ready-to-run R code chunk.
- Use as a cookbook for question types, validation, and logic.
- See [SurveyJS question types documentation](https://surveyjs.io/form-library/documentation/question) for the full range.

---

## Single Question Types

### Text Input

```{r}
surveyjs(
  schema = list(
    title = "Text Input",
    questions = list(
      list(type = "text", name = "name", title = "What is your name?")
    )
  )
)
```

### Comment Box

```{r}
surveyjs(
  schema = list(
    title = "Comment",
    questions = list(
      list(type = "comment", name = "feedback", title = "Your feedback?")
    )
  )
)
```

### Rating

```{r}
surveyjs(
  schema = list(
    title = "Rating",
    questions = list(
      list(type = "rating", name = "satisfaction", title = "How satisfied?")
    )
  )
)
```

### Dropdown

```{r}
surveyjs(
  schema = list(
    title = "Dropdown",
    questions = list(
      list(type = "dropdown", name = "country", title = "Country?", choices = list("USA", "Canada", "Other"))
    )
  )
)
```

### Checkbox

```{r}
surveyjs(
  schema = list(
    title = "Checkbox",
    questions = list(
      list(type = "checkbox", name = "fruits", title = "Pick fruits", choices = list("Apple", "Banana", "Cherry"))
    )
  )
)
```

### Radio Group

```{r}
surveyjs(
  schema = list(
    title = "Radio Group",
    questions = list(
      list(type = "radiogroup", name = "gender", title = "Gender", choices = list("Female", "Male", "Other"))
    )
  )
)
```

### Boolean Toggle

```{r}
surveyjs(
  schema = list(
    title = "Boolean",
    questions = list(
      list(type = "boolean", name = "agree", title = "Do you agree?")
    )
  )
)
```

---

## Multiple Choice & Matrix

### Matrix (Tabular Input)

```{r}
surveyjs(
  schema = list(
    title = "Satisfaction Matrix",
    questions = list(
      list(
        type = "matrix",
        name = "satisfaction",
        title = "How satisfied are you with...",
        rows = list("Quality", "Speed"),
        columns = list("Bad", "Okay", "Good")
      )
    )
  )
)
```

### Matrix Dropdown

```{r}
surveyjs(
  schema = list(
    title = "Matrix Dropdown",
    questions = list(
      list(
        type = "matrixdropdown",
        name = "skills",
        title = "Skill evaluation",
        columns = list(
          list(name = "experience", title = "Years", cellType = "dropdown", choices = 0:5)
        ),
        rows = list(
          list(value = "r", text = "R"),
          list(value = "python", text = "Python")
        )
      )
    )
  )
)
```

---

## Layout: Pages, Panels, Dynamic Forms

### Multi-Page Survey

```{r}
surveyjs(
  schema = list(
    title = "Multi-page Survey",
    pages = list(
      list(name = "page1", elements = list(
        list(type = "text", name = "first", title = "First Name")
      )),
      list(name = "page2", elements = list(
        list(type = "text", name = "last", title = "Last Name")
      ))
    )
  )
)
```

### Panels (Grouping Questions)

```{r}
surveyjs(
  schema = list(
    title = "Panel Example",
    questions = list(
      list(
        type = "panel",
        name = "personal_info",
        title = "Personal Information",
        elements = list(
          list(type = "text", name = "email", title = "Email"),
          list(type = "text", name = "phone", title = "Phone")
        )
      )
    )
  )
)
```

### Dynamic Panel

```{r}
surveyjs(
  schema = list(
    title = "Work History",
    questions = list(
      list(
        type = "paneldynamic",
        name = "jobs",
        title = "Previous Jobs",
        templateElements = list(
          list(type = "text", name = "employer", title = "Employer"),
          list(type = "text", name = "role", title = "Role")
        ),
        panelCount = 1
      )
    )
  )
)
```

---

## Advanced: Validation, Logic, Quizzes

### Required and Validated Input

```{r}
surveyjs(
  schema = list(
    title = "Validation Example",
    questions = list(
      list(
        type = "text", name = "email", title = "Email",
        isRequired = TRUE,
        validators = list(list(type = "email"))
      )
    )
  )
)
```

### Regex Validation

```{r}
surveyjs(
  schema = list(
    title = "Regex Validation",
    questions = list(
      list(
        type = "text", name = "code", title = "Code",
        validators = list(list(type = "regex", regex = "^[A-Z]{3}-\\d{3}$", text = "Format: AAA-999"))
      )
    )
  )
)
```

### Conditional Questions

```{r}
surveyjs(
  schema = list(
    title = "Conditional Example",
    questions = list(
      list(type = "radiogroup", name = "happy", title = "Are you happy?", choices = list("Yes", "No")),
      list(type = "comment", name = "whyNot", title = "Why not?", visibleIf = "{happy} = 'No'")
    )
  )
)
```

### Quiz

```{r}
surveyjs(
  schema = list(
    title = "Quiz",
    pages = list(
      list(elements = list(
        list(
          type = "radiogroup", name = "capital", title = "Capital of France?",
          choices = c("Berlin", "Paris", "Madrid"), correctAnswer = "Paris"
        )
      ))
    ),
    showProgressBar = "top",
    showCorrectAnswers = "true",
    completedHtml = "<h4>You scored {correctAnswers} out of {questionCount}.</h4>"
  )
)
```

---

## Initial Values & Read-only Mode

### Pre-fill Answers

```{r}
surveyjs(
  schema = list(
    title = "Pre-filled Survey",
    questions = list(
      list(type = "text", name = "name", title = "Name"),
      list(type = "rating", name = "rating", title = "Rating")
    )
  ),
  data = list(name = "Taz", rating = 5)
)
```

### Read-only Preview

```{r}
surveyjs(
  schema = list(
    title = "Read-only Preview",
    questions = list(
      list(type = "text", name = "name", title = "Name"),
      list(type = "rating", name = "rating", title = "Rating")
    )
  ),
  data = list(name = "Taz", rating = 5),
  read_only = TRUE
)
```

---

## Calculated Fields

```{r}
surveyjs(
  schema = list(
    title = "Sum Example",
    questions = list(
      list(type = "text", name = "a", title = "Enter a"),
      list(type = "text", name = "b", title = "Enter b"),
      list(type = "expression", name = "sum", title = "Sum", expression = "{a} + {b}")
    )
  )
)
```

---

## Static Content: Images & HTML

### HTML Block

```{r}
surveyjs(
  schema = list(
    title = "HTML Example",
    questions = list(
      list(type = "html", name = "intro", html = "<b>Welcome to the survey!</b>")
    )
  )
)
```

### Image

```{r}
surveyjs(
  schema = list(
    title = "Image Example",
    questions = list(
      list(type = "image", name = "logo", imageLink = "https://via.placeholder.com/300x100")
    )
  )
)
```

---

## Further Reference

- See the [Themes, Styling and Localization](themes-styling-and-localization.html) vignette for design tweaks.
- [SurveyJS Full Schema Reference](https://surveyjs.io/form-library/documentation/json-schema)
- [SurveyJS Question Types](https://surveyjs.io/form-library/documentation/question)
