---
title: "Themes, Styling and Localization"
description: "Make your surveys beautiful and multi-lingual with themes, CSS variables, and localization."
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Themes, Styling and Localization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

- _Change the look and feel of your survey with built-in or custom themes._
- _Tweak colors, fonts, and layout using CSS variables—all from R._
- _Instantly translate your survey UI for any audience._
- _For full schema and question options, see [Survey Schema Recipes]._
- _Tip: Can’t see your theme? Run `surveyjs_themes()` to check spelling!_

## Table of Contents

- [Themes: Built-in Styles](#themes-built-in-styles)
- [Custom Styling with CSS Variables](#custom-styling-with-css-variables)
- [List Available Themes](#list-available-themes)
- [Localization: Changing Survey Language](#localization-changing-survey-language)
- [Further Reference](#further-reference)

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width = 8
)
library(rsurveyjs)
```

## Themes: Built-in Styles

SurveyJS offers a variety of built-in themes to match modern UI patterns. Themes are well documented under [Themes & Styles](https://surveyjs.io/form-library/documentation/manage-default-themes-and-styles) from the original surveyjs documentation. General speaking every theme comes with a light/dark version and in a panel/panelless variant. For convenience all available themes are referenced under `surveyjs_themes()` within `rsurveyjs`.

### Using a built-in theme

```{r}
surveyjs(
  schema = list(
    title = "Modern Theme Example",
    questions = list(
      list(type = "text", name = "name", title = "Your name?"),
      list(type = "rating", name = "rating", title = "How was your experience?")
    )
  ),
  theme = "modern"
)
```

Try `"defaultV2"`, `"ThreeDimensionalLightPanelless"`, `"contrast-dark"`, `"flat-light"`, etc.
Custom Styling with CSS Variables

You can override [CSS variables](https://surveyjs.io/form-library/documentation/manage-default-themes-and-styles) to change colors, corners, fonts, and more.

### Example: Custom brand colors

```{r}
surveyjs(
  schema = list(
    title = "Custom Theme Colors",
    questions = list(
      list(type = "text", name = "team", title = "Your favorite team?")
    )
  ),
  theme = "DefaultLightPanelless",
  theme_vars = list(
    "--sjs-primary-backcolor" = "#0072B2",       # Custom blue
    "--sjs-primary-forecolor" = "#ffffff",       # White text
    "--sjs-corner-radius" = "14px",              # More rounded corners
    "--sjs-shadow-medium" = "0 4px 12px rgba(0,0,0,0.2)" # Softer shadow
  )
)
```

You can set any CSS variable supported by SurveyJS.
For the full list, see [SurveyJS theme variable docs].

## List Available Themes

You can list all available themes in rsurveyjs with:

```{r}
surveyjs_themes()
```

## Localization: Changing Survey Language

Easily switch the language of your survey UI for international audiences. (Note: _only_ technical key-words like "Complete" etc. get properly translated via the `locale` argument.) If you want more, see the multi-locale support section below.

### Example: German language

```{r}
surveyjs(
  schema = list(
    title = "Umfrage",
    questions = list(
      list(type = "rating", name = "zufriedenheit", title = "Wie zufrieden sind Sie?")
    )
  ),
  locale = "de"
)
```

### Supported Languages

SurveyJS supports many locales: `"en"`, `"de"`, `"fr"`, `"es"`, `"pt"`, `"ru"`, and more.
See [SurveyJS localization docs](https://surveyjs.io/form-library/documentation/localization#localization) for the full list.

### Multi-locale support

```{r}
surveyjs(
  schema = list(
    title = list(
      en = "Satisfaction Survey",
      fr = "Enquête de satisfaction"
    ),
    questions = list(
      list(
        type = "rating",
        name = "satisfaction",
        title = list(
          en = "How satisfied are you?",
          fr = "Êtes-vous satisfait ?"
        )
      ),
      list(
        type = "comment",
        name = "comments",
        title = list(
          en = "Additional comments",
          fr = "Commentaires supplémentaires"
        )
      )
    )
  ),
  locale = "fr"   # Try "en" or "fr"
)
```

## Further Reference

* [SurveyJS: Manage default themes and styles](https://surveyjs.io/form-library/documentation/manage-default-themes-and-styles)

* [SurveyJS: Localization](https://surveyjs.io/form-library/documentation/localization#localization)

* See also: [Survey Schema Recipes]()

